\Large \bf Webcam Fuzz Testing: Testing IoT Deployments

### 2015-12-10 Draft Paper/Draft_Paper.tex
Paper updates
Updated paper based on Kobus' feedback.

\subsection*{Abstract}
Fuzz testing, or fuzzing, is a simple, automated method to find bugs and vulnerabilities in programs, where random, potentially invalid inputs are sent. Fuzz testing can be much cheaper than other types of testing and often reveals bugs developers and testers cannot foresee. After reviewing some current research on fuzzing, we decided an interesting application would be to test `Internet of Things' (IoT) devices like IP cameras. We believe that fuzzing a network-connected device can reveal interesting bugs or vulnerabilities, and in the case of security cameras, some of these vulnerabilities may be serious. We use fuzzing methods on two different types of Wi-Fi cameras in order to evaluate the efficacy of fuzz testing on these recent types of IoT deployments. We used Pathoc within a Bash shell script framework for crafted malice towards the HTTP servers in these cameras, and ran over 250,000 fuzzing tests. We did identify several interesting events and responses from fuzzing tests, but did not identify any critical bugs or serious vulnerabilities in the cameras.

The specific `call for papers' that we target in the presentation of this research is the 9th USENIX Workshop on Offensive Technologies (WOOT '15).

\section{Introduction}
\subsection{Motivation}

@@

\subsection{Problem}
We began this project with some general understanding of fuzzing as a test tool, but without a clear vision of what network services might be interesting or valuable to fuzz. After an initial period of exploring current research in fuzzing, we settled on the ultimate goal of our project: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} The project involved several steps: choosing a service to test; deciding how to generate random inputs; determining how to distinguish "good" and "bad" test results; implementing the random tester; and evaluating the effectiveness of the test procedure.

In this project, we started with the goal to design, implement and evaluat an automated tester for a networking service. This is meant to evaluate the value of fuzz testing on a network, with the goal of hopefully finding a previously undiscovered bug. A very basic and highly proliferated technology deployed on the internet is an HTTP server. But because of this prevalence, popular servers such as Apache have been thoroughly tested and documented. However, more and more devices are being connected, with an uptake in the Internet of Things (IoT) mentality. Therefore, we chose wireless IP cameras as the platform to fuzz test. These are some of the most widely available IoT devices for consumers. We found that the two devices we purchased ran basic HTTP servers, and we could use tools made for these applications.

One reason we thought it would be interesting as well as important to test these IP cameras is because they are widely used in security systems today. It would likely be a bad thing if an outsider could shut down or otherwise impair the function of your security cameras. One main goal we had during this experiment was to identify security vulnerabilities in the cameras through fuzzing, to find out if a potential attacker could impair the camera's function.

\section{Related Work}
In the beginning stages of our project, we explored some recent papers related to fuzzing, to give us a more clear idea of how this test technique is currently implemented and how it is evolving. Some of the more interesting papers we came across are detailed below.

@@

We tried to find research related to fuzzing internet-connected devices, but were unable to. Therefore, we thought this might be a good starting point for our research. We thought this would be interesting because more and more `things' are connecting to the internet today, and all of these `Internet of Things' devices have network protocols that would be interesting to test.

\section{Experiment Setup}
In this section we describe details about the setup of our experiment, the
cameras we used, how we gathered information and discovered interesting ways to fuzz test them, and the tools and programs that aided us.

@@

Though the cameras boasted support for many network protocols, most of the functionality was very limited and only supported client protocols. Both cameras did have small HTTP servers, though, which we felt were much more interesting to fuzz, as they will more readily accept the inputs that we would give them.

The first step we took in identifying network protocols that would be interesting and `fuzzable' was to capture some traffic from the cameras in Wireshark~\cite{wireshark}. We also looked at the HTML source behind the web pages to discover potential attack points. We discovered early on that authentication tokens could be easily exposed, making deeper application level access possible. This was possible because the cameras only used Basic or Digest Authentication, where the encoded user name and password are stored in plain text in the requests. From here, we could automate the fuzzer to get past the HTTP ``front door" and send sensitive commands that require authentication. This way, we could also test the application layer being run on these camera, rather than the HTTP protocol layer. We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions, and we used these pages to fuzz application layers.

@@

\subsection{Platforms}
The primary vehicle for running Pathoc in a Bash script was using Oracle's VM VirtualBox 5.0.10 running on two separate Windows 10 laptops. One computer ran a 32-bit Ubuntu 12.04 VM with 2.0GiB of dedicated RAM. The other computer was using the All-in-one SDN App Development Starter VM, an image based off of 64-bit Ubuntu 14.04, from SDNHub.org.

@@

\section{Results}
We began this project with this question in mind: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} At this point in our research, we have not identified any critical bugs in the cameras or inputs that would completely disable the system. We did, however, identify several events or responses that are of interest. We were watching the video output of the cameras during some of the fuzz testing, and we did notice some freezing and lagging of the video feed. We did not record video or attempt to qualify the video output at this stage of our project.

>>>>

\subsection*{Abstract}
Fuzz testing, or fuzzing, is a simple, automated method to find bugs and vulnerabilities in programs, where random, potentially invalid inputs are sent. Fuzz testing can be much cheaper than other types of testing and often reveals bugs developers and testers cannot foresee. After reviewing some current research on fuzzing, we decided an interesting application would be to test `Internet of Things' (IoT) devices like IP cameras. With the growing proliferation of these IoT devices, they could become a very attractive target for malicious attacks. Attacks on these devices would also greatly compromise security. We use fuzzing methods on two different types of Wi-Fi cameras in order to evaluate the efficacy of fuzz testing on these recent types of IoT deployments. We used a fuzzing tool called Pathoc within a Bash shell script framework for crafted malice towards the HTTP servers in these cameras, and ran over 250,000 fuzzing tests. We did identify several interesting events and responses from fuzzing tests, but did not identify any critical bugs or serious vulnerabilities in the cameras.

The specific `call for papers' that we target in the presentation of this research is the 9th USENIX Workshop on Offensive Technologies (WOOT '15). \url{https://www.usenix.org/conference/woot15/call-for-papers}

\section{Introduction}

@@

After an initial period of exploring current research in fuzzing, we settled on this goal: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} Reaching this goal involved several steps: choosing a service to test; deciding how to generate random inputs; determining how to distinguish "good" and "bad" test results; implementing the random tester; and evaluating the effectiveness of the test procedure.

Initially, we set out to design our own fuzzer, but in researching the subject showed that may tools were already available, which allowed us to focus on trying to find undiscovered bugs and vulnerabilities, instead of the effectiveness of an implementation. A very basic and highly proliferated technology deployed on the internet is an HTTP server. But because of this prevalence, popular servers such as Apache have been thoroughly tested and documented. However, more and more devices are being connected, with an uptake in the Internet of Things (IoT) mentality. Therefore, we chose wireless IP cameras as the platform to fuzz test. These are some of the most widely available IoT devices for consumers, and could become an attractive entry point for attackers. We found that the two devices we purchased ran basic HTTP servers, and we could use tools made for these applications. If these devices could be accessed by unauthorized third parties, or be made unable to perform their duties, this could be a serious issue. We believe that fuzz testing can be an effective way to study if these bugs or vulnerabilities exist.

\section{Related Work}
An important first step into researching this process is to obtain a more clear idea of how this test technique was created, hoe it is currently implemented, and how it is evolving.

@@

We tried to find research related to fuzzing internet-connected devices, but were unable to. Therefore, we thought this might be a good starting point for our research. We thought this would be important because more and more `things' are connecting to the internet today, and all of these `Internet of Things' devices have network protocols that would be interesting to test.

\section{Experimental Methodology}
In order to create meaningful experiments, the devices under test had to be purchased and evaluated further. Points of attack had to be gathered, evaluated, and implemented in the available tools in order to better attempt to find interesting results.

@@

While the many supported protocols provided many different access points, it was important to identify how the protocol was being implemented. The majority of services running on the cameras were client protocols, such as sending SMTP mail or an image transfer via FTP. This then gave greater incentive in focusing on the HTTP protocol, as it was the only server. The nature of a server is very appealing to an attack, as it is readily available to accept user inputs, and the biggest ``front door" to the cameras.

The first step we took in identifying points of access that could be `fuzzable' was to capture some traffic from the cameras in Wireshark~\cite{wireshark}. We also looked at the HTML source behind the web pages to discover potential attack points. We discovered early on that authentication tokens could be easily exposed, making deeper application level access possible. This was possible because the cameras only used Basic or Digest Authentication, where the encoded user name and password are stored in plain text in the requests. From here, we could automate the fuzzer to get past the HTTP ``front door" and send sensitive commands that require authentication. This way, we could also test the application layer being run on these camera, rather than the HTTP protocol layer. We discovered several `.cgi' pages under the main HTML pages that were the primary interfaces to the camera functions, and we used these pages to fuzz application layers.

@@

\subsection{Platforms}
The primary vehicle for running Pathoc was a Bash script running on a virtual Linux machine inside Oracle's VM VirtualBox 5.0.10. Two different Windows 10 laptops were used to run the VMs. One computer ran a 32-bit Ubuntu 12.04 VM with 2.0GiB of dedicated RAM. The other computer was using the All-in-one SDN App Development Starter VM, an image based off of 64-bit Ubuntu 14.04, from SDNHub.org.

@@

\section{Results}
We began our research with this question in mind: \textit{Can we use fuzzing to discover interesting bugs or vulnerabilities in a network-connected device?} At this point in our research, we have not identified any critical bugs in the cameras or inputs that would completely disable the system. We did, however, identify several events or responses that are of interest. We were watching the video output of the cameras during some of the fuzz testing, and we did notice some freezing and lagging of the video feed. We did not record video or attempt to qualify the video output at this stage of our project.
